Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-07-17 manuscripts/manuscript.Rmd
rerun manuscript

```{r}
fraction_no_shift <- function(x)
 sum(x[2:length(x)] - x[1:length(x)-1] == 0)/length(x)

@@

While still not common for the particular parameter combinations we examine,
we find that positive unaltered quotas through time are much more likely
to occur when optimizing against $\Pi_1$ where policy adjustment costs
scale linearly with the size of proposed policy changes: in the 100 replicates
of data presented above the harvest policy is identical in conecutive intevals
only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
`r no_shifts[["L1"]] * 100`$ with linear costs $Pi_1$ and `r no_shifts[["fixed"]]*100`%
for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
these costs ($c_1$) increases.

@@

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost-free adjustment optimum, NPV0.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}
table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
table1_long$reduction <- as.factor(table1_long$reduction)
ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
write.csv(table1_long, "components/data/figure6.csv")
```

@@

```{r Table1, results="asis"}
who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
table1 <- arrange(error_df[who], reduction) 
names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")
pandoc.table(table1, caption=caption)
```

>>>>

```{r}
fraction_no_shift <- function(x){
 nonzeros <- which(x > 0)
 x <- x[nonzeros]
 sum(x[2:length(x)] - x[1:length(x)-1] == 0)/length(x)
}

@@

While still not common for the particular parameter combinations we examine,
we find that positive unaltered quotas through time are much more likely
to occur when optimizing against $\Pi_1$ where policy adjustment costs
scale linearly with the size of proposed policy changes: in the 100 replicates
of data presented above the harvest policy is strictly positive and identical in consecutive intervals
only `r no_shifts[["L2"]] * 100`% of the time for quadratic costs $\Pi_2$, compared with
`r no_shifts[["L1"]] * 100` with linear costs $\Pi_1$ and `r no_shifts[["fixed"]]*100`%
for fixed costs $\Pi_3$. Moreover, these occurrences increase in frequency as the severity of
these costs ($c_1$) increases.

@@

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue), shown by penalty function over increasing magnitudes of cost.  All values are relative to the cost-free adjustment optimum, NPV0.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present. The severity of the latter mistake increases sharply as adjustment costs make a larger fraction of the total costs."}

who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "reduction")
table1 <- arrange(error_df[who], reduction) 
names(table1) = c("penalty.fn", "ignoring", "assuming", "reduction")

table1_long <- melt(table1, id = c('penalty.fn', 'reduction'))
table1_long$reduction <- as.factor(table1_long$reduction)
ggplot(table1_long, aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + facet_wrap(~reduction) 
write.csv(table1_long, "components/data/figure6.csv")
```

@@

```{r Table1, results="asis"}
pandoc.table(table1, caption=caption)
```
